# Vignette Changes

```{r loadReqPackages}
require(RVignetteChanges)
```


### Examples of running Bioconductor

Below is the code used to scrape through the `Bioconductor` **SVN** repository to check for the presence of vignettes. This was run weekly.

```{r runBioconductor, eval=FALSE}
outPath <- "~/Documents/projects/personal/RVignettePackageDownloads/bioconductor"
devRepo <- "https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/"
relRepo <- "https://hedgehog.fhcrc.org/bioconductor/branches/RELEASE_2_12/madman/Rpacks/"

usePWD <- "readonly:readonly"

devPacks <- getBiocPackages(devRepo, usePWD)
dev2 <- strtrim(devRepo, nchar(devRepo) - 1)
devStatus <- checkBiocPackages(devPacks, dev2, usePWD)
.sessionInfo <- sessionInfo()
.timeDate <- Sys.time()
save(devStatus, .sessionInfo, .timeDate, file=outFile)

relPacks <- getBiocPackages(relRepo, usePWD)
rel2 <- strtrim(relRepo, nchar(relRepo) - 1)
relStatus <- checkBiocPackages(relPacks, rel2, usePWD)

filePart <- paste("biocStatus_", format(Sys.Date(), "%d.%m.%y"), sep="")
outFile <- file.path(outPath, filePart)
.sessionInfo <- sessionInfo()
.timeDate <- Sys.time()
save(relStatus, devStatus, .sessionInfo, .timeDate, file=outFile)
```

### CRAN

This is the code used to find new and updated packages on a `CRAN` mirror, and download them to a new directory based on the date. This was also run weekly

```{r runCran, eval=FALSE}
outPath <- "~/Documents/projects/personal/RVignettePackageDownloads/cran/"
setwd(outPath)
load("allPackages.RData")
options(repos="http://ftp.ussg.iu.edu/CRAN/")
currPackages <- available.packages()

allList <- rownames(allPackages)
currList <- rownames(currPackages)

currINall <- currList %in% allList
allINcurr <- allList %in% currList
currNew <- currList[!currINall]

allVer <- allPackages[allList[allINcurr], "Version"]
currVer <- currPackages[allList[allINcurr], "Version"]

diffVer <- currVer != allVer
diffPackages <- names(diffVer)[diffVer]

saveDir <- format(Sys.Date(), "%d.%m.%y")
dir.create(saveDir)
fullPath <- file.path(outPath, saveDir)
downloadedPackages <- download.packages(pkgs=diffPackages, destdir=fullPath)

allPackages <- currPackages
fileCurr <- file.path(fullPath, "downloadedPackages.RData")
.sessionInfo <- sessionInfo()
.timeDate <- Sys.time()

save(downloadedPackages, currPackages, .sessionInfo, .timeDate, file=fileCurr)

allPackages <- currPackages
fileAll <- file.path(outPath, "allPackages.RData")
save(allPackages, file=fileAll) 
```


## Analysis

What we want to do is for each snapshot that we have, go in and find out if we have:

  * vignette at all
  * type of vignette
  
```{r examineData}
biocPath <- "~/Documents/projects/personal/RVignettePackageDownloads/bioconductor"
filePattern <- "biocStatus"

biocMatrices <- biocValues2Matrix(biocPath, filePattern)
biocDev <- biocMatrices$dev
biocRelease <- biocMatrices$rel
biocQueries <- biocMatrices$queries

.sessionInfo <- sessionInfo()
.timeDate <- Sys.time()
save(biocDev, biocRelease, biocQueries, .sessionInfo, .timeDate, file="inst/data/bioconductorData.RData")
```
